---
title: "Data sources"
output: html_document
---

## Data sources

### Geography codes

```{r}
# unzip("data-raw/key-stage-4-performance-revised_2021-22.zip",
#       exdir = "data/KS4")
geogs <- readr::read_csv("data/KS4/data/2122_lad_pr_data.csv")

geogs |>
  dplyr::filter(region_code == "E12000003") |> 
  dplyr::select(region_code, region_name, lad_code, lad_name) |> 
  unique() |> 
  View()
```

## UKPRN full lookup is here: https://get-information-schools.service.gov.uk/Establishments/Search?tok=8TQILM6z

```{r ukprn-lookup}
# unzip("data-raw/Schools etc UKPRN full register lookup.zip", exdir = "data/UKPRN_lookup.csv")

ukprn <- readr::read_csv("data/UKPRN_lookup.csv/results.csv")

onspd <- readr::read_csv("~/Data/Geodata/ONSPD/ONSPD_NOV_2022_UK/Data/ONSPD_NOV_2022_UK.csv")

ukprn |> dplyr::left_join(onspd, by = c("Postcode" = "pcds")) |> 
  dplyr::filter(is.na(oslaua)) |> View()


dplyr::inner_join(fe$`fes-et-provider-enrolments-202122-q4.csv`,
                  ukprn,
                  by = c("provider_ukprn" = "UKPRN"))
```




```{r}
geog_codes <- list(wy = paste0("E080000", 32:36),
                   ny = c("E0600000014", # York
                          paste0("E070001", 63:69) # Craven:Selby
                   )
)
```

### Leicester and Leicestershire LSIP
Dashboard: https://www.insight-unlocked.co.uk/
Report: https://www.insight-unlocked.co.uk/pdfs/leicester-and-leicestershire-lsip-report.pdf
Annex: https://www.insight-unlocked.co.uk/pdfs/leicester-and-leicestershire-lsip-annexes.pdf

#### Skills supply
Key stage 4: https://explore-education-statistics.service.gov.uk/find-statistics/key-stage-4-performance-revised

```{r}
ks4 <- readr::read_csv("data/KS4/data/2122_lad_pr_data.csv") |> 
  dplyr::filter(lad_code %in% c(geog_codes$wy, geog_codes$ny))
```


A-level: https://explore-education-statistics.service.gov.uk/find-statistics/a-level-and-other-16-to-18-results

```{r}
# unzip("data-raw/a-level-and-other-16-to-18-results_2021-22.zip",
#       exdir = "data/A-level")

a_level <- lapply(list.files("data/A-level/data", full.names = TRUE),
                  function(file) {
                    readr::read_csv(file) |> 
                      dplyr::filter(new_la_code %in% c(geog_codes$wy, geog_codes$ny))
                  }) |> 
  setNames(basename(list.files("data/A-level/data")))
```

FE: https://explore-education-statistics.service.gov.uk/find-statistics/further-education-and-skills

```{r}
# unzip("data-raw/further-education-and-skills_2021-22.zip",
#       exdir = "data/FE")

fe <- lapply(list.files("data/FE/data", full.names = TRUE),
             function(file) {
               df <- readr::read_csv(file)
               if ("lad_code" %in% names(df)) {
                 df <- dplyr::filter(df, lad_code %in% c(geog_codes$wy, geog_codes$ny))
               }
               return(df)
             }) |> 
  setNames(basename(list.files("data/FE/data")))
```


16-18 Destination Measures: https://explore-education-statistics.service.gov.uk/find-statistics/16-18-destination-measures

```{r}
# unzip("data-raw/16-18-destination-measures_2020-21.zip",
#       exdir = "data/FE_destination")

fe_dest <- lapply(list.files("data/FE_destination/data", full.names = TRUE),
                  function(file) {
                    readr::read_csv(file) |>
                      dplyr::filter(new_la_code %in% c(geog_codes$wy, geog_codes$ny))
                  }) |> 
  setNames(basename(list.files("data/FE_destination/data")))
```

Higher education: https://www.hesa.ac.uk/support/definitions/students

### Change of data definitions
NB Three types of student record data file exist: 051, 054, 056
051 (student record) has been used for historic data, up to and including 18/19.
054 (alternative student record) is used for 19/20 to current latest (20/21), but 051 is also available for this period. Main difference is a different course classification system.
056 will be introduced for Future publications (21/22 onwards, due to drop in Feb 23) and will not have options of 051 or 054 available.

### Available detailed tables (HESA)

```{r hesa-tables-available}
hesa_tables <- rvest::read_html("https://www.hesa.ac.uk/data-and-analysis/students/releases") |> 
  rvest::html_elements("#detailedtables") |> 
  rvest::html_table()
```

## ID UKPRN of providers in the two areas

```{r}
ukprn_he_yorks <- table51 |> dplyr::select(UKPRN, `HE provider`, `Region of HE provider`) |> 
  dplyr::filter(`Region of HE provider` == "Yorkshire and The Humber") |> 
  dplyr::distinct() |> 
  dplyr::mutate(LSIP = dplyr::case_when(UKPRN %in% c("10007785",
                                                     "10007148",
                                                     "10021682",
                                                     "10003854",
                                                     "10003861",
                                                     "10034449",
                                                     "10007795",
                                                     "10003863") ~ "WY",
                                        UKPRN %in% c("10004740",
                                                     "10007713",
                                                     "10007167") ~ "NY",
                                        TRUE ~ NA_character_)) |> 
  dplyr::filter(!is.na(LSIP))
```



```{r}
# Table 1
table1.url <- "https://www.hesa.ac.uk/data-and-analysis/students/table-1.csv"

download.file(table1.url, file.path("data-raw", "HESA", "table-1.zip"), mode = "wb")

unzip("data-raw/HESA/table-1.zip", exdir = "data/HESA/table-1")

table1.files <- list.files("data/HESA/table-1", full.names = TRUE)

table1 <- lapply(table1.files, function(file) {
  readr::read_csv(file, skip = 14)
}) |> dplyr::bind_rows()
```


```{r table-13-49}

# Table 13 - HE student enrolments by HE provider and subject of study 2014/15 to 2018/19

table13.url <- "https://www.hesa.ac.uk/data-and-analysis/students/table-13.csv"

download.file(table13.url, "data-raw/HESA/table-13.zip", mode = "wb")
unzip("data-raw/HESA/table-13.zip", exdir = "data/HESA/table-13")

table13.files <- list.files("data/HESA/table-13", full.names = TRUE)
table13 <- lapply(table13.files, function(file) {
  readr::read_csv(file, skip = 14)
}) |> 
  dplyr::bind_rows()

# Table 49 - HE student enrolments by HE provider and subject of study 2019/20 to 2020/21

table49.url <- "https://www.hesa.ac.uk/data-and-analysis/students/table-49.csv"

download.file(table49.url, "data-raw/HESA/table-49.zip", mode = "wb")
unzip("data-raw/HESA/table-49.zip", exdir = "data/HESA/table-49")

table49.files <- list.files("data/HESA/table-49", full.names = TRUE)

table49 <- lapply(table49.files, function(file) {
  readr::read_csv(file, skip = 14)
})
```

```{r}

# Table 19 - HE qualifiers by HE provider and subject of study 2014/15 to 2018/19 (051)
# Table 51 - HE qualifiers by HE provider and subject of study 2019/20 to 2020/21 (051, 054)

table19.url <- "https://www.hesa.ac.uk/data-and-analysis/students/table-19.csv"
table19.zip <- "data-raw/HESA/table-19.zip"
table19.path <- "data/HESA/table-19"

download.file(table19.url, table19.zip, mode = "wb")
unzip(table19.zip, exdir = table19.path)

table19.files <- list.files(table19.path, full.names = TRUE)

table19 <- lapply(table19.files, function(file) {
  readr::read_csv(file, skip = 14)
}) |> 
  dplyr::bind_rows()

table51.url <- "https://www.hesa.ac.uk/data-and-analysis/students/table-51.csv"
download.file(table51.url, "data-raw/HESA/table-51.zip", mode = "wb")
unzip("data-raw/HESA/table-51.zip", exdir = "data/HESA/table-51")
table51.files <- list.files("data/HESA/table-51", full.names = TRUE)

table51 <- lapply(table51.files, function(file) {
  readr::read_csv(table51.files, skip = 13)
}) |> 
  dplyr::bind_rows()
  
table51_051.url <- "https://www.hesa.ac.uk/data-and-analysis/students/table-51-051.csv"
download.file(table51_051.url, "data-raw/HESA/table-51-051.zip", mode = "wb")
unzip("data-raw/HESA/table-51-051.zip", exdir = "data/HESA/table-51-051")
table51_051.files <- list.files("data/HESA/table-51-051", full.names = TRUE)
table51_051 <- lapply(table51_051.files, function(file) {
  readr::read_csv(file, skip = 13)
}) |> 
  dplyr::bind_rows()

```


No of students by provider
Science/non-science
full-time/part-time
Number by subject and level (first degree UG, other UG, PGR, PGT)
Number by subject of study (CAH level 1 and 3)
Top ten major subject areas (level 1)
No of students by level of study
Students by HE provider

Enrolments by gender
EU, non-EU, UK




IfATE KSBs (Knowledge, Skills, Behaviours); https://www.instituteforapprenticeships.org/apprenticeship-standards/?

#### Skills Demand

HE graduates: https://www.hesa.ac.uk/support/definitions/graduates

Businesses, Jobs and Skills: Companies House, NOMIS, Lightcast advertised in place/radius

Industry Forecast: Lightcast (jobs and historical establishments (UKBC?))

Occupation Forecast: Lightcast (Jobs, Growth, Replacements, Openings) + forecast

Top Title and Skills: Lightcast (Common skills, special skills, certifications)

Sentiment: IfATE website, word cloud on common traits, etc.

#### Business Survey results

Ask Ruth to share their data for inclusion?
